The SMT Competition 2015--2018

### 2018-10-08 2018/report/SMT-COMP.tex
Some introduction

\jsatheading{1}{2004}{25-30}
\ShortHeadings{The SMT Competition 2015--2018}
{TODO et al.}
\firstpageno{25}

@@

\author{\name{Sylvain Conchon (co-organizer, 2015--2016)}
\email{Sylvain.Conchon@lri.fr} \\
\addr Affiliation \\
City \\
Country
\AND
\name{David D\'{e}harbe (co-organizer, 2015--2016)}
\email{david@dimap.ufrn.br} \\
\addr Federal University of Rio Grande do Norte \\
Natal \\
Brazil
\AND
\name{Matthias Heizmann (co-organizer, 2016--2018)}
\email{heizmann@informatik.uni-freiburg.de} \\
\addr Affiliation \\
City \\
Country
\AND
\name{Aina Niemetz (co-organizer, 2018)}
\email{niemetz@cs.stanford.edu} \\
\addr Affiliation \\
City \\
Country
\AND
\name{Giles Reger (co-organizer, 2017--2018)}
\email{giles.reger@manchester.ac.uk} \\
\addr Affiliation \\
City \\
Country
\AND
\name{Tjark Weber (competition chair, 2015--2018)}
\email{tjark.weber@it.uu.se} \\
\addr Uppsala University \\
Uppsala \\
Sweden}

@@

\begin{abstract}
\TODO
\end{abstract}

@@

>>>>

\jsatheading{1}{2004}{25-30}
\ShortHeadings{The SMT Competition 2015--2018}
{Weber et al.}
\firstpageno{25}

@@

\author{%
  \name{Tjark Weber (competition chair, 2015--2018)}
  \email{tjark.weber@it.uu.se} \\
  \addr Uppsala University \\
  Uppsala \\
  Sweden
  \AND
  \name{Sylvain Conchon (co-organizer, 2015--2016)}
  \email{Sylvain.Conchon@lri.fr} \\
  \addr Affiliation \\
  City \\
  Country
  \AND
  \name{David D\'{e}harbe (co-organizer, 2015--2016)}
  \email{david@dimap.ufrn.br} \\
  \addr Federal University of Rio Grande do Norte \\
  Natal \\
  Brazil
  \AND
  \name{Matthias Heizmann (co-organizer, 2016--2018)}
  \email{heizmann@informatik.uni-freiburg.de} \\
  \addr Affiliation \\
  City \\
  Country
  \AND
  \name{Aina Niemetz (co-organizer, 2018)}
  \email{niemetz@cs.stanford.edu} \\
  \addr Affiliation \\
  City \\
  Country
  \AND
  \name{Giles Reger (co-organizer, 2017--2018)}
  \email{giles.reger@manchester.ac.uk} \\
  \addr Affiliation \\
  City \\
  Country}

@@

\begin{abstract}
  The International Satisfiability Modulo Theories Competition is an
  annual competition between Satisfiability Modulo Theories solvers.
  We report on the design and selected results of the competition
  during the last FLoC Olympiad, from 2015 to 2018. \TODO: some
  notable observations/conclusions?
\end{abstract}

@@

Satisfiability Modulo Theories (SMT) is a generalization of Boolean
satisfiability (SAT), the satisfiability decision problem for
propositional logic.  In place of Boolean variables, SMT formulas may
contain terms that are built from function and predicate symbols drawn
from a number of background theories.  Background theories, which are
typically motivated by application areas, include the theory of
arrays, integer and real arithmetic, bit-vectors, and floating-point
numbers among others.  For instance, the following is an SMT formula
over the combination of integer arithmetic and uninterpreted
functions:
$$TODO$$
Software tools to determine the satisfiability of such formulas are
called SMT solvers.

Internally, many SMT solvers employ SAT solving techniques to deal
with the propositional structure of the formula, and combine these
with (semi-)decision procedures for the background theories that the
solver supports~\cite{TODO,TODO,TODO}.  Historically, SMT solvers have
focused on quantifier-free formulas and decidable combinations of
background theories.  Increasingly, however, SMT solvers also support
quantified formulas.  Hence there is overlap between SMT solving and
automated theorem proving for quantified Boolean formulas (QBF),
first-order logic, and even higher-order logic~\cite{TODO}.

The International Satisfiability Modulo Theories Competition
(SMT-COMP) is an annual competition between SMT solvers.  It is
affiliated with the International Workshop on Satisfiability Modulo
Theories.  Solvers are submitted to the competition by their
developers, and pitted against each other in a number of tracks and
divisions.  The SMT Competition was part of the Federated Logic
Conference (FLoC) Olympic Games in~2014, and again in~2018.  It was
last described in a 2014 competition report~\cite{TODO}.  In this
paper, we report on the design and selected results of the competition
during the last FLoC Olympiad, from 2015 to 2018.

  structure of the paper
\end{tjark}
